Applying State-free Reversible VAMPNets and Markov State Models to Learn Dynamics of DNA Oligonucleotides

### 2020-12-10 manuscript.tex
spellcheck

% need to discuss tmelt shift
We measured the slow dissociation response by fitting the distribution of times at which the core base pairs separate beyond a 2 nm cutoff. We found the inverse of these relaxation times -- the effective dissociation rate -- to increase exponentially with temperature, which is expected given the large enthalpic barrier of dissociation \citep{Craig1971ElaxationOligon,Porschke1971CooperativeTransition,Williams1989LaserDGCATGC}. We noted an average temperature shift of about 4C between experiment and simulation exponentials. While 3spn2 captures melting temperature relatively well, some deviation is expected given varied ion conditions and other coarse-grained effects. We used to this temperature shift to inform our equilibrium simulations in the proceeding section. We also noted an acceleration of about one order of magnitude compared to experiment, although this factor is sensitive to the exact definition of melting temperature. After accounting for the melting temperature shift and acceleration factor, we saw strong agreement between the experimental data and simulated relaxation fits. At lower temperatures, T-jump slow responses likely contain a mix of dissociation and hybridization dynamics, therefore rates do not drop off to the same extent as our analysis which considers dissociation alone. GC-core showed the largest deviation from experiment, indicating that increased temperature triggers dissociation at a disproportionately higher rate in simulation compared to experiment.

@@

Following the analysis pipeline described above, we generate SRV-MSMs for each sequence. We identified seven kinetically relevant states that are captured within the resolution of the model. Figure \ref{fig:allseq_table} shows cartoon and molecular rendering for each of these states as well as their sequence-specific stationary probabilities. By row, these include the fully hybridized state (H) in which all native base pairings are intact, four "shifted" states (5S1, 3S1, 5S2, 3S2) where complementary base pairs form out-of-register, a frayed state (F4), unique to GC-core, in which the four terminal A:T base pairs are unbound, and the fully dissociated state (D). Figure \ref{fig:allseq_transition} shows how these states fit into sequence-specific low-dimensional representations and kinetic models. Arrows between states show the conditional transition probability to another state within the MSM lag time. We now proceed to analyse the sequence-dependent thermodynamics and kinetic features of each MSM.

@@

Experimentally, out-of-register states are suspected to occur, but are difficult to capture due to short lifetimes and similarity in response to other processes such as fraying. To explicitly minimize out-of-register base pairing, similar AT repeat motif sequences have been padded by GCG clamps during experimental analysis \cite{Wyer2014KineticsAT-tracts}. Recent all-atom results identified analogous out-of-register states as "deep kinetic traps" along the hybridization pathway for repetitive dGCGCGC hexamers \citep{Xiao2019}. Contrary to our kinetic results, however, "slithering" mechanisms along out-of-register tracts were not observed to be a dominant pathway, especially when compared to the high rates of slithering exhibited by the homogenous dGGGGGG strand. It is unclear whether these differences were a consequence of varied simulation conditions or whether GC repeat motifs are less susceptible to direct out-obref-register transitions compared to AT motifs. This is possible given that stronger hydrogen binding in GC motifs \citep{Yakovchuk2006Base-stackingHelix,Zacharias2020Base-PairingFormation} may prevent fluctuation-driven rearrangement, however further computational and experimental studies are required to verify these differences.

@@

In addition to identifying relaxation timescales, the T-jump IR response profile can inform the distribution of dynamics contributing to the response. In particular, the fast response of AT-all and GC-end exhibits more stretched exponential character than for GC-core and GC-mix  (Figure \ref{fig:Fig6}). Furthermore, the GC-end response contains both G:C and A:T vibrational contributions, suggesting that native terminal base fraying may not be the unique source of the response. On the other hand, GC-mix and GC-core are characterized by a distinct fast response comprised only of A:T features that points to A:T fraying as the predominant dynamic source. We predict that the mid-IR responses of fraying and shifting are not clearly distinguishable for GC-ends and AT-all, therefore we cannot determine the stretched responses originate from fraying dynamics in out-of-register configurations, shifting mechanisms during the dissociation process, or some combination of the two. Although reproducing stretched signals is not within the scope of this analysis, we see qualitative agreement between more complex transition network (AT-all > GC-end > GC-core ~ GC-mix) and increased stretching in the fast response.

@@

The F4 state is more accessible from an already bound helix, and once oligos are in F4, they are over 20x more likely to return to H than to D. Thus once a D $\leftrightarrow$ F4 transition has occurred, a F4 $\leftrightarrow$ H transition will likely proceed. On the other hand, H $\leftrightarrow$ F4 events are more frequent but unlikely to initiate complete dissociation. We previously noted that frayed dynamics are substantially accelerated in the 3spn2 model, which may lead to the F4 state being sampled more frequently then in experiment. Because GC-core stability is most sensitive to fraying, this effect could cause GC-core to dissociate more frequently and lead to the deviation in slow response we note in figure 2.

% discuss computational comparisons needs work
Lattice model studies have shown that frayed intermediates make substantial contributions to the GC-core conformational ensemble \citep{Araque2016LatticeCooperativity, Phys2019,Sanstead2020OxidizedDNA}. Araque et al. defines a similar 8-mer sequence (dATGCGCAT) as non-two-state, where a stable, symmetrically A:T frayed state is a crucial part of the duplex transition path \citep{Araque2016LatticeCooperativity}. When examining all four sequences using T-jump IR and 2D IR spectroscopy, Sanstead et al. found that the GC-core had the highest deviation from two-state behavior during dissociation (when excluding out-of-register contributions) \citep{Sanstead2016}. As T-jump IR data only showed a loss of A:T contacts during the fast response, this intermediate state was defined by a high degree of fraying about the central core. While 1-2 base pair fraying was commonly observed for GC-mix and AT-all as well, lattice model predictions showed that GC-core had substantially more frayed base pairs \citep{Phys2019}. Variable T-jump measurements and Smoluchowski simulations on model 1D free energy landscapes showed that AT termini fraying was an effectively barrierless process characterized by rapid inter-conversion between all accessible frayed states \citep{Sanstead2018DirectDehybridization}. We see the same rapid fraying in simulation data -- which is too fast to be attributed to a converged SRV mode -- however our SRV-MSM results show this inter-conversion first relies on the slower formation of the the A:T bond nearest to the GC center.  Although this process occurs much slower than single A:T base bonding and breaking, it may be difficult to experimentally discern from the overall hybridization process which contains both G:C and A:T character and occurs on a similar timescale.

@@

\begin{figure} %[ht!]
	\begin{center}
	\includegraphics[width=150mm, scale=1]{Fig7.pdf}
        \caption{WC base pair distance and molecular renderings along two representative GC-mix hybridization and dissociation events. Permutable distances are reflected across the x-axis and show that fraying in the hybridized states tends to occur independently on either end of the duplex until fully dissociation occurs. The SRV-MSM state is shown along the x-axis, indicating the point at which a transition has been determined. Fluctuation between states is common during the transition.}
        \label{fig:GC-mix_transitions}
	\end{center}
\end{figure}

@@

To supplement GC-mix analysis, we looked at qualitative trends in our trajectory data near hybridization and dissociation events, paying close attention to the distances between matching WC-pairs (Figure \ref{fig:GC-mix_transitions}). During hybridization, we observed the formations of some key base pair contacts before the full duplex formed. Specifically, first contacts tended to involve one of the G:C bonds and at least one neighboring A:T. This behavior is indicative of a nucleation-zippering mechanism as has been reported in previous studies \citep{Wetmur1968KineticsDNA, Porschke1971CooperativeTransition, Yin2011KineticsHybridization}. For dissociation events, we noted two base pair fraying on one or both sides of the duplex followed by more rapid dissociation of the central base pairs. There's evidence of a short-lived state composed of 2-4 base pair contacts immediately before full dissociation occurs. In contrast to the F4 state we observe in GC-core, these conformations do not form a distinct free-energy minima in SRV or tICA space, nor do they tend to reform intact duplexes. As a whole, these dynamics are similar to previously reported "fraying-peeling" mechanism \citep{Wong2008TheSimulations, Perez2010Real-timeUnfolding, Zgarbova2014BaseRNA}. We observed similar fast dynamics and transition states in the other three sequences, however they are more difficult to discern as they occur in concert with the longer lasting metastable states discussed above.

@@

Although our SRV-MSMs provide useful insight into slow processes, we were also interested in the ensemble of configurations within PCCA+ macrostates and during transition periods. These configurations interchange significantly faster than the SRV and MSM lag times, but we can use a diffusion map embedding to glean a structural understanding of the macrostate population. Diffusion maps generate a low dimensional embedding of the data into high variance structural modes and are well-suited to find subtle differences in temporally disconnected data \citep{Coifman2006DiffusionMaps, Ferguson2010SystematicMaps}.

While examining molecular renderings, we noticed that a significant proportion of GC-end 5s1 configurations retained one native G:C bond, even when all available A:T bonds were formed out-of-register. We would not necessarily expect duplexes to sacrifice helical conformational entropy in order to facilitate termini bonding. To compare how these state populations differ between GC-end and AT-all, we employed diffusion maps built on an equal sampling of 5000 conformations from the 5S1 state of both sequences. We used all 100 intermolecular distances (as opposed to the 55 permutation free coordinates used to construct SRV-MSM) as our distance metric, making it easier to discern structures that form on either permutable end of the shifted conformation. This created degenerate 2nd and 3rd diffusion modes, with nearly equal eigenvalues, differentiating effects at the identical "top" and "bottom" of the strands. In Figure \ref{fig:GC-end_dmaps} we present the first two non-trivial diffusion map eigenfunctions and show representations of the degenerate third coordinate in the SI (Figure \ref{fig:GC-end_dmaps_full}). Diffusion maps built from samples of the 3S1 states are also shown in the SI (Figure \ref{fig:GC-end_dmaps_3prime}).

@@

Once we determined a strong hybridization coordinate, we compared probability distributions for each sequence along $\Psi_2$ (Figure \ref{fig:Fig8}). The $ <\Psi_2 < 0$ reflects the distance between approaching strands, but we noted statistically meaningful differences between sequence once first WC contacts are made. In the $ 0.001 <\Psi_2 < 0.0035$ region, heatmaps show that contacts tend to form near the center of the duplex, and frayed structures progressively zipper closed as $<\Psi_2$ increases. As expected, GC-core shows a distinct peak in the frayed region, corresponding to the F4 macrostate identified by SRV-MSMs. GC-mix has a notably higher population than AT-all and GC-end but displays a more gradual progression toward the native hybridized state. This is consistent with the downhill nucleation-zippering mechanism described above. Although differences between AT-all and GC-end are more subtle, overall sequence populations in this region follow predictions by Sanstead et. al. regarding deviations from two-state binding behavior, where GC-core > GC-mix > AT-all > GC-end \citep{Sanstead2016}. This qualitative agreement shows that MSM information can be adapted to compare sequences along common pathways and elucidate dynamics occurring faster than the lag time. Furthermore, we are able to distinguish out-of-register deviations from fraying deviations and describe relevant experimental comparisons for each.

@@

We have demonstrated how G:C placement in an otherwise repetitive AT sequence has a profound impact on equilibrium hybridization dynamics. By supplementing coarse-grained MD with data-driven time-lagged analysis, we constructed high resolution SRV-MSMs capable of distinguishing sequence-dependent kinetic behavior. In particular, we found that AT-all and GC-end sequences both participate in some degree of out-of-register base pair shifting, although these states have higher kinetic relevance for AT-all. On the other hand, GC-core hybridization transits through, or is perhaps facilitated by, a frayed intermediate in which one half of A:T bonds are broken and the duplex is significantly disrupted. Our computational approach and results show strong comparisons T-jump experiments at ns and us timescales. Going forward, we expect that this work will be extended to predict more general trends in sequence-dependent hybridization and motivate strategies for experimental comparisons. These insights should be leveraged for sequence design and incorporated into the growing field of dynamic DNA nanotechnology.

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=120mm, 
        scale=0.5]{Figs/figs_imp/allseq_event_count.png}
        \caption{All sequences consist of 20 trajectories initialized in the hybridized states and 20 in dissociated state. The fraction of hybridized duplexes averaged across these sets is shown over time. For all sequences these curves converge near 0.5, but stochasticity of rare-event makes a definitive Tmelt difficult to identify. The number of hybridization/dissocation combined across trajectories is shown. Not every trajectory contained a transition event, but on average more than one full event occurred (H$\rightarrow$D$\rightarrow$H) per trajectory, providing adequate sampling of dynamics. AT-all undergoes substantially more transition, but many of these do not reach a native (in-register) hybridized state.}
        \label{fig:allseq_event_count}
	\end{center}
\end{figure}

>>>>

% need to discuss tmelt shift
We measured the slow dissociation response by fitting the distribution of times at which the core base pairs separate beyond a 2 nm cutoff. We found the inverse of these relaxation times -- the effective dissociation rate -- to increase exponentially with temperature, which is expected given the large enthalpic barrier of dissociation \citep{Craig1971ElaxationOligon,Porschke1971CooperativeTransition,Williams1989LaserDGCATGC}. We noted an average temperature shift of about 4C between experiment and simulation exponentials. While 3spn2 captures melting temperature relatively well, some deviation is expected given varied ion conditions and other coarse-grained effects. We used this temperature shift to inform our equilibrium simulations in the proceeding section. We also noted an acceleration of about one order of magnitude compared to experiment, although this factor is sensitive to the exact definition of melting temperature. After accounting for the melting temperature shift and acceleration factor, we saw strong agreement between the experimental data and simulated relaxation fits. At lower temperatures, T-jump slow responses likely contain a mixture of dissociation and hybridization dynamics, therefore rates do not drop off to the same extent as our analysis which considers dissociation alone. GC-core showed the largest deviation from experiment, indicating that increased temperature triggers dissociation at a disproportionately higher rate in simulation compared to experiment.

@@

Following the analysis pipeline described above, we generated SRV-MSMs for each sequence. We identified seven kinetically relevant states that are captured within the resolution of the model. Figure \ref{fig:allseq_table} shows cartoon and molecular rendering for each of these states as well as their sequence-specific stationary probabilities. By row, these include the fully hybridized state (H) in which all native base pairings are intact, four "shifted" states (5S1, 3S1, 5S2, 3S2) where complementary base pairs form out-of-register, a frayed state (F4), unique to GC-core, in which the four terminal A:T base pairs are unbound, and the fully dissociated state (D). Figure \ref{fig:allseq_transition} shows how these states fit into sequence-specific low-dimensional representations and kinetic models. Arrows between states show the conditional transition probability to another state within the MSM lag time. We now proceed to analyse the sequence-dependent thermodynamics and kinetic features of each MSM.

@@

Experimentally, out-of-register states are suspected to occur, but are difficult to capture due to short lifetimes and similarity in response to other processes such as fraying. To explicitly minimize out-of-register base pairing, similar AT repeat motif sequences have been padded by GCG clamps during experimental analysis \cite{Wyer2014KineticsAT-tracts}. Recent all-atom results identified analogous out-of-register states as "deep kinetic traps" along the hybridization pathway for repetitive dGCGCGC hexamers \citep{Xiao2019}. Contrary to our kinetic results, however, "slithering" mechanisms along out-of-register tracts were not observed to be a dominant pathway, especially when compared to the high rates of slithering exhibited by the homogenous dGGGGGG strand. It is unclear whether these differences were a consequence of varied simulation conditions or whether GC repeat motifs are less susceptible to direct out-of-register transitions compared to AT motifs. This is possible given that stronger hydrogen binding in GC motifs \citep{Yakovchuk2006Base-stackingHelix,Zacharias2020Base-PairingFormation} may prevent fluctuation-driven rearrangement, however further computational and experimental studies are required to verify these differences.

@@

In addition to identifying relaxation timescales, the T-jump IR response profile can inform the distribution of dynamics contributing to the response. In particular, the fast response of AT-all and GC-end exhibits more stretched exponential character than for GC-core and GC-mix  (Figure \ref{fig:Fig6}). Furthermore, the GC-end response contains both G:C and A:T vibrational contributions, suggesting that native terminal base fraying may not be the unique source of the response. On the other hand, GC-mix and GC-core are characterized by a distinct fast response comprised only of A:T features that points to A:T fraying as the predominant dynamic source. We predict that the mid-IR responses of fraying and shifting are not clearly distinguishable for GC-ends and AT-all, therefore we cannot determine the stretched responses originate from fraying dynamics in out-of-register configurations, shifting mechanisms during the dissociation process, or some combination of the two. Although reproducing stretched signals is not within the scope of this analysis, we see qualitative agreement between more complex transition network (AT-all $>$ GC-end $>$ GC-core, GC-mix) and increased stretching in the fast response.

@@

The F4 state is more accessible from an already bound helix, and once oligos are in F4, they are over 20x more likely to return to H than to D. Thus once a D $\rightarrow$ F4 transition has occurred, a F4 $\rightarrow$ H transition will likely proceed. On the other hand, H $\rightarrow$ F4 events are more frequent but unlikely to initiate complete dissociation. We previously noted that frayed dynamics are substantially accelerated in the 3spn2 model, which may lead to the F4 state being sampled more frequently then in experiment. Because GC-core stability is most sensitive to fraying, this effect could cause GC-core to dissociate more frequently and lead to the deviation in slow response we note in figure 2.

% discuss computational comparisons needs work
Lattice model studies have shown that frayed intermediates make substantial contributions to the GC-core conformational ensemble \citep{Araque2016LatticeCooperativity, Phys2019,Sanstead2020OxidizedDNA}. Araque et al. defines a similar 8-mer sequence (dATGCGCAT) as non-two-state, where a stable, symmetrically A:T frayed state is a crucial part of the duplex transition path \citep{Araque2016LatticeCooperativity}. When examining all four sequences using T-jump IR and 2D IR spectroscopy, Sanstead et al. found that the GC-core had the highest deviation from two-state behavior during dissociation (when excluding out-of-register contributions) \citep{Sanstead2016}. As T-jump IR data only showed a loss of A:T contacts during the fast response, this intermediate state was defined by a high degree of fraying about the central core. While 1-2 base pair fraying was commonly observed for GC-mix and AT-all as well, their lattice model predicted GC-core to have substantially more frayed base pairs \citep{Phys2019}. Variable T-jump measurements and Smoluchowski simulations on model 1D free energy landscapes showed that AT termini fraying was an effectively barrierless process characterized by rapid inter-conversion between all accessible frayed states \citep{Sanstead2018DirectDehybridization}. We see the same rapid fraying in simulation data -- which is too fast to be attributed to a converged SRV mode -- however our SRV-MSM results show this inter-conversion first relies on the slower formation of the the A:T bond nearest to the GC center.

%Although this process occurs much slower than single A:T base bonding and breaking, it may be difficult to experimentally discern from the overall hybridization process which contains both G:C and A:T character and occurs on a similar timescale.

@@

\begin{figure} %[ht!]
	\begin{center}
	\includegraphics[width=170mm, scale=1]{Fig7.pdf}
        \caption{WC base pair distance and molecular renderings along two representative GC-mix hybridization and dissociation events. Permutable distances are reflected across the x-axis and show that fraying in the hybridized states tends to occur independently on either end of the duplex until full dissociation occurs. The SRV-MSM state is shown along the x-axis, indicating the point at which a transition has been determined. Fluctuation between states is common during the transition.}
        \label{fig:GC-mix_transitions}
	\end{center}
\end{figure}

@@

To supplement GC-mix analysis, we looked at qualitative trends in our trajectory data near MSM-identified hybridization and dissociation events. We present two representative events in Figure \ref{fig:GC-mix_transitions} along with all native base pair distances over time. During hybridization, we observed the formations of some key base pair contacts before the full duplex formed. Specifically, first contacts tended to involve one of the G:C bonds and at least one neighboring A:T. This behavior is indicative of a nucleation-zippering mechanism as has been reported in previous studies \citep{Wetmur1968KineticsDNA, Porschke1971CooperativeTransition, Yin2011KineticsHybridization}. For dissociation events, we noted two base pair fraying on one or both sides of the duplex followed by more rapid dissociation of the central base pairs. There's evidence of a short-lived state composed of 2-4 base pair contacts immediately before full dissociation occurs. In contrast to the F4 state we observe in GC-core, these conformations do not form a distinct free-energy minima in SRV space, nor do they tend to reform intact duplexes. As a whole, these dynamics are similar to previously reported "fraying-peeling" mechanism \citep{Wong2008TheSimulations, Perez2010Real-timeUnfolding, Zgarbova2014BaseRNA}. We observed similar fast dynamics and transition states in the other three sequences, however they are more difficult to discern as they occur in concert with the longer lasting metastable states discussed above.

@@

Although our SRV-MSMs provide useful insight into slow processes, we were also interested in the ensemble of configurations within PCCA+ macrostates and during transition periods between states. These configurations interchange significantly faster than the SRV and MSM lag times, but we can use a diffusion map approach to glean a structural understanding of the macrostate population. Diffusion maps generate a low dimensional embedding of the data into high variance structural modes and are well-suited to find subtle differences in temporally disconnected data \citep{Coifman2006DiffusionMaps, Ferguson2010SystematicMaps}.
% add something here on previous dmap refs?

While examining molecular renderings, we noticed that a significant proportion of GC-end 5s1 configurations retained one native G:C bond, even when all available A:T bonds were formed out-of-register. We would not necessarily expect duplexes to sacrifice helical conformational entropy in order to facilitate termini bonding. To compare how these state populations differ between GC-end and AT-all, we employed diffusion maps built on an equal sampling of 5000 conformations from the 5S1 state of both sequences. We used all 100 intermolecular distances (as opposed to the 55 permutation free coordinates used to construct SRV-MSM) as our distance metric, making it easier to discern structures that form on either permutable end of the shifted conformation. This created degenerate 2nd and 3rd diffusion modes, with nearly equal eigenvalues, differentiating effects at the identical "top" and "bottom" of the strands. In Figure \ref{fig:GC-end_dmaps} we present the first two non-trivial diffusion map eigenfunctions and show representations of the degenerate third coordinate in the SI. Diffusion maps built from samples of the 3S1 states are also shown in the SI.

@@

Once we determined a strong hybridization coordinate, we compared probability distributions for each sequence along $\Psi_2$ (Figure \ref{fig:Fig8}). The region where $\Psi_2 < 0$ is noisy and mainly reflects the distance between approaching strands, but we noted statistically meaningful differences between sequence populations once first WC contacts are made. In the $ 0.001 <\Psi_2 < 0.0035$ region, heatmaps show that contacts tend to form near the center of the duplex, and frayed structures progressively zipper closed as $\Psi_2$ increases. As expected, GC-core shows a distinct peak in the frayed region, corresponding to the F4 macrostate identified by SRV-MSMs. GC-mix has a notably higher population than AT-all and GC-end but displays a more gradual progression toward the native hybridized state. This is consistent with the downhill nucleation-zippering mechanism described above. Although differences between AT-all and GC-end are more subtle, overall sequence populations in this region follow predictions by Sanstead et. al. regarding deviations from two-state binding behavior, where GC-core > GC-mix > AT-all > GC-end \citep{Sanstead2016}. This qualitative agreement shows that MSM information can be adapted to compare sequences along common pathways and elucidate dynamics occurring faster than the lag time. Furthermore, we are able to distinguish out-of-register deviations from fraying deviations and describe relevant experimental comparisons for each.

@@

We have demonstrated how G:C placement in an otherwise repetitive AT sequence has a profound impact on equilibrium hybridization dynamics. By supplementing coarse-grained MD with data-driven time-lagged analysis, we constructed high resolution SRV-MSMs capable of distinguishing sequence-dependent kinetic behavior. In particular, we found that AT-all and GC-end sequences both participate in some degree of out-of-register base pair shifting, although these dynamics are more relevant for AT-all. On the other hand, GC-core hybridization transits through, or is perhaps facilitated by, a frayed intermediate in which one half of A:T bonds are broken and the duplex is significantly disrupted. Our computational approach and results show strong comparisons to T-jump experiments at ns and us timescales. Going forward, we expect that this work will be extended to predict more general trends in sequence-dependent hybridization and motivate strategies for experimental comparisons. These insights should be leveraged for sequence design and incorporated into the growing field of dynamic DNA nanotechnology.

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=120mm, 
        scale=0.5]{Figs/figs_imp/allseq_event_count.png}
        \caption{All sequences consist of 20 trajectories initialized in the hybridized states and 20 in dissociated state. The fraction of hybridized duplexes averaged across these sets is shown over time. For all sequences these curves converge near 0.5, but stochasticity of rare-event makes a definitive $T_m$ difficult to identify. The number of hybridization/dissocation combined across trajectories is shown. Not every trajectory contained a transition event, but on average more than one full event occurred (H$\rightarrow$D$\rightarrow$H) per trajectory, providing adequate sampling of dynamics. AT-all undergoes substantially more transition, but many of these do not reach a native (in-register) hybridized state.}
        \label{fig:allseq_event_count}
	\end{center}
\end{figure}
